---
title: "Title of Analysis Goes Here"
author: "Your Name (netid@illinois.edu)"
date: "Insert Date Here"
output:
  html_document: 
    theme: default
    toc: yes
---

```{r, setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.align = 'center')
```

```{r, load-packages, include = FALSE}
# load packages
```

```{r read-data, warning = FALSE, message = FALSE}
# read subset of data
pitches_2019_regular_04 = readr::read_csv("data/pitches-2019-regular-04.csv")
pitches_2019_regular_05 = readr::read_csv("data/pitches-2019-regular-05.csv")
pitches_2019_regular_06 = readr::read_csv("data/pitches-2019-regular-06.csv")
pitches_2019_regular_07 = readr::read_csv("data/pitches-2019-regular-07.csv")
pitches_2019_regular_08 = readr::read_csv("data/pitches-2019-regular-08.csv")
pitches_2019_regular_09 = readr::read_csv("data/pitches-2019-regular-09.csv")
pitches_2019_post = readr::read_csv("data/pitches-2019-post.csv")
```

```{r}
# merge regular season data
pitches_2019_regular = dplyr::bind_rows(
  pitches_2019_regular_04,
  pitches_2019_regular_05,
  pitches_2019_regular_06,
  pitches_2019_regular_07,
  pitches_2019_regular_08,
  pitches_2019_regular_09
)
```

***

## Abstract

> Abstract text goes here.

***

## Introduction

Write your introduction here.

***

## Methods

Describe the methods used in this section.

### Data

Specifically describe the data and how it is used here.

### Modeling

Discuss your modeling and validation strategy here.

***

## Results

State your results here.

***

## Discussion

Discuss your results here.

***

## Appendix

Place potential additional information here.
